### 2020-04-20 intro.tex
Added references to the Introduction and fixed a few things in the Introduction.

The Cray XK7 Titan supercomputer was the \#1 system in the world for a
very long time, and has remained a critically important computer
system through the end of its life in the Summer of 2019. It defied
scale with 18,688 individual compute nodes and delivered tens of
billions of computing hours to the U.S. Department of Energy
mission-critical programs for nearly 7 years.

@@

The failures were traced to a failing resistor on the circuitboard
(not the GPU iself) While the 2016 resistor failures were a surprise, there is a known
phenomenon \cite{referenceneeded} that describes a two phase process
that leads to failure. It also explains why there was a very stable
period preceeding the failures. There is specific decay associated
with the electronic components where, as these products age, they will
eventually fail thresholds for guard band margin and other things. In
a lot of cases, they will just fail as well. \fix{Give a reference and
  expand?}

>>>>

The Cray XK7 Titan supercomputer~\cite{olcf:titan} was the \#1 system in the world for a
very long time~\cite{top500list}, and has remained a critically important computer
system through the end of its life in the Summer of 2019. It defied
scale with 18,688 individual compute nodes and delivered tens of
billions of computing hours to the U.S. Department of Energy
mission-critical programs for nearly 7 years.

@@

The failures were traced to a failing resistor on the circuitboard
(not the GPU iself). While the 2016 resistor failures were a surprise, there is a known
phenomenon~\cite{referenceneeded} that describes a two phase process
that leads to failure. It also explains why there was a very stable
period preceding the failures. There is specific decay associated
with the electronic components where, as these products age, they will
eventually fail thresholds for guard band margin and other things. In
a lot of cases, they will just fail as well. \fix{Give a reference and
  expand?}
